
% The Basics

% Create article
\documentclass{article}
\begin{document}
This is my \emph{first} document prepared in \LaTeX.
I typed it on \today.

% New paragraph
We have seen that to typeset something in \LaTeX, we type in the
text to be typeset together with some \LaTeX\ commands.
Words must be separated by spaces (does not matter how many)
and lines maybe broken arbitrarily.

% Paragraph without indentation
\noindent The end of a paragraph is specified by a \emph{blank line}
in the input. In other words, whenever you want to start a new
paragraph, just leave a blank line and proceed.

% Extra space after period - '\@'
Carrots are good for your eyes, since they contain Vitamin A\@.
Have you ever seen a rabbit wearing glasses?

% No extra space after period - '\ '
The numbers 1, 2, 3, etc.\ are called natural numbers.
According to Kronecker, they were made by God; all else being the work of Man.

% Explicit space after command
I think \LaTeX\ is fun.

% Opening and closing quotes
Note the difference in right and left quotes in `single quotes' and ``double quotes".

% Various types of dashes
X-rays are discussed in pages 221--225 of Volume 3---the volume on
electromagnetic waves.

% Accent
% Dotless 'i' and 'j' - \i, \j
\'{E}l est\'{a} aqu\'{\i}.

% Symbols
Maybe I have now learnt about 1\% of \LaTeX :
\$, \textbackslash, \#, \ss, \O, \AE, \l, \L, ?`.\\
Break 1.\\[10pt] Break 2. % Optional argument to \\

% Environment
\begin{center}
The \TeX nical Institute\\[.75cm]
Certificate
\end{center}
\noindent This is to certify that Mr. N. O. Vice has undergone a
course at this institute and is qualified to be a \TeX nician.
\begin{flushright}
The Director\\
The \TeX nical Institute
\end{flushright}

% Type style is specified by family, series and shape
\textit{roman family, medium series, italic shape type.}
\textbf{roman family, boldface series, upright shape type.}

% Combine family, series and shape
\textrm{\textsl{roman family, medium series, slanted shape.}}

% Command \emph and italic shape
\textit{A polygon of three sides is called a \emph{triangle} and a
polygon of four sides is called a \emph{quadrilateral}}

% Change style with command or declaration
By a \textbf{triangle}, we mean a polygon of three sides.
By a {\bfseries triangle}, we mean a polygon of three sides.

% Declaration name as environment name
\begin{sffamily}
These declaration names can also be used as environment names.
\end{sffamily}

% Type size
{\scriptsize scriptsize} {\small small} {\Large Large}

% Break current page
\pagebreak

% Combine style changes with size changes
\begin{center}
{\bfseries\huge The \TeX nical Institute}\\[1cm]
{\scshape\LARGE Certificate}
\end{center}
\noindent This is to certify that Mr. N. O. Vice has undergone a
course at this institute and is qualified to be a \TeX nical Expert.
\begin{flushright}
{\sffamily The Director\\
The \TeX nical Institute}
\end{flushright}

\end{document}

